\iflandscape{}{\vfil}
\subsection{Aircraft}
\label{sec:Aircraft}

Aircraft are independent units and therefore require no leader unit. They also move differently from other units: an aircraft unit may place itself on any zone on the map when its turn to act comes up.

Aircraft are automatically spotted when they are on the map.

Aircraft movement is different from other units:

Aircraft begin on the \LAUNCH\ box of the Re-arm track.

While on the Re-arm track, an aircraft unit may make Movement rolls to pro\-gress along the track.

An aircraft on the \LAUNCH\ box at the beginning of its turn may be placed on any zone on the map. Its turn is now over.

Once an aircraft acts while on the map (usually in the turn after it has moved there), it is returned to the RE-ARM box of the Re-arm track.

An aircraft unit on the map may act as any other unit except that it may not make a Movement roll.

Aircraft have a 4-cap Skill column. Aircraft units have one Skill at rank 4, one at rank 3, one at rank 2, and one at rank 1. They have a \Morale\ track one box long. If the unit has \Veteran\ Skill 1 or 2, the \Morale\ track is two boxes long. If the unit has \Veteran\ Skill 3 or 4, then the Morale track is three boxes long.

The maximum movement for aircraft is zero zones as they are not represented on the map. Aircraft units do not move on the map in the same fashion as ground units and so do not make Movement rolls except to decrease their re-arm time.

Aircraft increase range by 1 for all distance calculations (both against them and against other targets).

Aircraft can only be attacked by the Anti-air Skill.

