\section{Stress Tracks}
\label{sec:Stress Tracks}

Every character has three stress tracks: Health, Composure, and Wealth. Each has a relevant Skill that can modify the number of boxes in the track. Some Stunts can modify the number of boxes as well. The Health track is associated with the Stamina Skill. Composure is associated with Resolve. Wealth is associated with Assets.

Tracks start out with three boxes in them, which represents a character untrained in the relevant Skill. If the relevant Skill is 1 or 2, the track is 4 boxes; if it is 3 or 4, the track is 5 boxes; if it is 5, the track has 6 boxes.

\begin{description}
\item[Health]~

The Health stress track represents how close you are to sustaining an injury that will affect your performance and require time to recover from. It does not represent actual injury. The Health stress track is modified by Stamina.

The Health stress track takes hits when a character loses a combat check --- he takes a bullet, gets burned by a laser, is cut by a knife, or is punched in the eye. It's not an effective injury unless it causes a Consequence --- there is no mechanical effect to having a box filled in a track. It's when boxes you don't have get filled that you have trouble.

\item[Composure]~

The Composure stress track represents how close you are to mental breakdown. It does not represent the degree of actual breakdown. The Composure stress track is modified by Resolve.

The Composure stress track takes hits when a character loses a social combat check and sometimes when under fire in combat. As with Health, it's not an effective hit until a Consequence is applied.

\item[Wealth]~

The Wealth stress track represents how close you are to having real financial trouble. It does not represent actual debt or financial ruin but rather how close you are to feeling the ramifications of debt. The Wealth stress track is modified by Assets.

The Wealth stress track takes hits when a character fails a Wealth check when buying something or assisting with monthly ship maintenance. It follows all the same rules as the other stress tracks do, though recovery can take longer.

\end{description}

\input{chapter/03/subsec-consequences}
\input{chapter/03/subsec-taken-out}
\input{chapter/03/subsec-concessions}

