\section{Skills}\label{sec:skills} % \href{sec:id76}

\input{sidebar/original-material-skills}

\rulebox{Players select 15 skills for their character}
Players select 15 skills for their character and rank them in the \textbf{pyramid}: one at level 5, two at 4, three at 3, four at 2, and five at 1.

Selected Skills should be logically consistent with the character's background material as elaborated in the Aspects phases but there are no hard and fast rules for selection. Skills are selected so that they are appropriate for the characters about whom we've now learned quite a lot (with even more existing in the players' imaginations). Players will also select three Stunts (see below). Some players may prefer to select their Stunts before their Skills, or at the same time. This process may require some revision of Aspects or some redefinition of character direction.

One approach for new players is to choose an apex Skill first --- what the character does best. Stunts may follow from that. Finally, the size of the various hit tracks is calculated. This process might take another 20-30 minutes perhaps, yielding completed characters.

There are many Skills from which characters can choose, most of which represents a specific area of learned knowledge. Each Skill is presented with a brief overview, and some idea of what a character choosing this Skill as their apex might be. In each case, though, the precise range of a given Skill's effect is to be determined by the referee in consultation with the table.

\rulebox{``Untrained'' skill use is at level -1}
An attempt to use any Skill that is not in the character's Skill pyramid does so at an effective Skill level of -1.

Within this list, there are three classes of Skills that have been identified explicitly.

\begin{description}
\item[Combat Skills]~

represent the ability to use a weapon in personal combat; other Skills are of course useful in combat (Agility, Alertness), but do not convey the ability to use a weapon.

\item[Space Skills]~

represent the ability to fill a position on a spaceship that is relevant to space combat; other Skills are of course useful in space (Aircraft, EVA), but do not convey specific Skills relevant to the space combat mini-game.

\item[Track Skills]~

Further, three Skills (Assets, Resolve, and Stamina) have a direct impact on the length of a character's stress tracks: with these three Skills alone, an untrained character is considered to have a default of zero for the purposes of determining stress track length (i.e. a character untrained in Resolve will still have three boxes in their Composure stress track); checks on these Skills are still made at -1.
\end{description}

Most characters will want at least one combat Skill and one space Skill, or will have a good story for why they do not.

\input{chapter/03/subsec-skill-descriptions}
\input{sidebar/weapon-familiarity}
\input{chapter/03/subsec-some-special-skills}

