\subsection{Skill Descriptions}

\begin{description}
\item[Agility]
measures how fast, flexible, and dexterous a character is. Use Agility to throw for accuracy (opposed attack roll to hit someone with a rock), to dodge an attack (opposed roll against an attack roll), or to vault a fence (fixed difficulty). It is most typically used as a movement check in combat.

Apex: an acrobat or similar athlete; his speed and precision of movement are legendary.

\item[Aircraft]
the ability to pilot all forms of aircraft, including interface vehicles into low orbit.

Apex: a pilot capable of daredevil stunts and precision aerobatics that win awards.

\item[Alertness]
determines just how on the ball a character is. Alertness checks might be made to establish whether a character spots a hidden character (opposed roll, Alertness against Stealth) or to fix an order of action in combat.

Apex: unsurprisable, the character with apex Alertness might be a highly trained martial artist or a highly skilled observer such an investigator or military scout.

\item[Animal Handler]
represents the ability to control, break, and ride animals (as appropriate) on all worlds for which the character has Culture/Tech.

Apex: a master of animals, perhaps running a circus or someone with a preternatural ability to commune with animals.

\item[Archaeology]
archaeology in the cluster is the study of earlier civilizations, before the most recent fall. An archaeologist might possess broken fragments of knowledge of higher tech, the residue that might have survived the inevitable collapse, on all worlds for which the character has Culture/Tech. Note that Archaeology in a cluster is not strictly an academic pursuit. In fact in most cases it is not academic at all --- it can be industrial, technical, and secretive. In a sense it is closer to prospecting than what we think of as archaeology, hence its division from the Science Skill.

Apex: an intuitive locator of artifacts, able to find signs of ancient habitations in the slightest perturbation of orbit or change in colour of foliage; his past finds are legendary and probably dangerous.

\item[Arts]
understanding of the literature, history, and fine arts on all worlds for which the character has Culture/Tech.

Apex: a renowned researcher and teacher in her field whose opinion is sought after by others whenever controversy arises, or a highly-skilled creative genius.

\item[Assets (track)]
the Assets Skill is the only way to be rich. Money is never tracked independently. It is used in practically any roll related to a purchase and it establishes the length of the character's Wealth stress track. It models the availability of cash, but also contacts, convertible properties, loans, and even an ability to evade debt collection.

Apex: a tycoon with the resources of worlds to bring to bear. Small worlds, mind you, but worlds.

\item[Brawling (combat)]
fists, feet, found weapons.

Apex: the Brawler might be an accomplished professional fighter, a spiritual martial arts specialist, or a military trainer. She might also just be someone with a lot of experience in crummy bars.

\item[Brokerage]
knowledge of interstellar trade and how to manipulate it. Directly assists ship maintenance Assets checks if ships are hauling cargo or passengers.

Apex: the Broker is a legend amongst traders and speculators of any system she has passed through. She always finds a bargain and always finds a desperate buyer and, when times are really tough, she knows how to make her own luck. After all when she makes a decision, whole stock markets follow.

\item[Bureaucracy]
a facility with handling the people and paperwork associated with government and other institutional processes. Use your Bureaucracy Skill when filing for a license to mine an asteroid or to find the person responsible for paying out your slipship insurance.

Apex: taking Bureaucracy as a apex Skill flags the character as a professional pusher of paper, certainly, but more interestingly a professional pusher of people in a professional, procedural context; this is the kind of person that knows how to game corporate and government processes to get what he wants from people who attend more closely to their procedures and paperwork than the reality of what they are doing. Which is most everyone.

\item[Charm]
sometimes you want to sway your opposition on looks and a smile. Whatever you want and wherever that might lead, Charm is your one-on-one persuasion Skill.

Apex: the apex Charmer might be a celebrity, trading on her status and fame to persuade, or might be one of those smooth, naturally friendly people that everyone just wants to please. Either way she is legendary for it, whether through fame or infamy, or just police rap sheets for fraud and confidence tricks.

\item[Close Combat (combat)]
knives, swords, spears, etc.

Apex: the Close Combat specialist can always find a use for an apparently archaic weapon. He's the one that knows the gladius is the best possible boarding weapon as long as the defenders don't have pikes (or fusion cannons), but, more, he's confident (and correct) that he can get inside a shooter's guard before the trigger is pulled. He might be a famous swordsman (an entertainer or a duellist) or he might be a low-profile but in-demand trainer for military or private interests.

\item[Communications (space)]
different from the Computer Skill, Communications uses communication and computer assets and is primarily offensive: it's about hacking, subverting, destroying, or otherwise incapacitating data and data carrying systems. In the space combat system, Communications is used to augment Electronic Warfare attack and defense rolls. Outside of that system it might be used for all manner of nefarious and destructive communications --- jamming, hacking, eavesdropping, spoofing, and so on.

Apex: the Communication specialist has communication equipment with her at all times, ready to communicate with anything even if she has to jury rig a solution to do it; once in communication she owns the channel, capable of manipulating its contents and endpoints to her own needs. She's a security specialist wearing both hats and may be famous, infamous, and/or wanted by the police.

\item[Computer (space)]
the computer engineer is the one coping with da\-ta-re\-la\-ted disasters. He wrote the security policy and he can repair and restore in real time. In space combat, this Skill is used as part of the damage control phase.  Outside of space combat it might be used to evaluate data system, use a sophisticated computer to find some hidden data, or reprogram a device to perform a new function.

Apex: Computer as a apex Skill describes a person obsessed with the detail of computer function and operation, possibly at the expense of application knowledge. In deep multi-collapse databases he might even be a kind of archaeologist, able to dredge up obscure ancient algorithms and craft them to the current purpose to great effect. Every problem looks like a computer problem to the Computer specialist, and it often is --- he's the guy that wired the airlock to ignore safety interlocks and blow those boarders out of the hull, and then fixed it afterwards.

\item[Culture/Tech]
represents the facility of the character with culture and technology of a given system in the cluster.

Apex: Culture/Tech is a special Skill and having it as an apex Skill is more of a quantitative statement than qualitative: you have travelled widely, and are at home in most systems in the cluster; you might even be able to pass yourself off as a native of somewhere else.

\item[Demolitions]
an understanding and experience with the controlled use of explosives and related devices. This Skill would pertain at least as much to defusing explosives as to setting them off and includes knowledge of effective use of the explosives for demolition and excavation: you know how much to put where in order to get the effect you want.

Apex: the Demolitions guy gets the most done with the least; he can manufacture efficient explosives from stuff in the ship's locker, and can use those improvised explosives to destroy a bridge because he also knows the weak points on such structures.

\item[Energy Weapons (combat)]
lasers, plasma weapons, lightning guns, or anything else that does harm with energy.

Apex: energy weapons are only really efficient at T2 and above, so the Energy Weapons expert is an unusual enthusiast for this specific kind of weapon. She takes advantage of obscure features of her preferred weapon type, like the zero flight time and the high energy density in storage on the device, to get every ounce of advantage --- she shoots down drones, sets low-power lasers on overload so they explode, can get energy from one device to another, can modulate the power on a laser to use it as a communicator, and hits everything she aims at. Her fascination with the specific form of weapon likely borders on nerdish.

\item[Engineering (space)]
your ship's engineer is the guy that keeps the hulk in space, moving, and at a temperature you can all live with. He's also the guy that repairs damage from battle or accident and generally knows what's where. In space combat, this Skill is used as part of the damage control phase, to repair damage to the Frame stress tracks on spacecraft. Outside of space combat it might be used to fix Consequences on a ship, assess the state of a vessel, or make a gadget related to spacecraft and their drives and power plants.

Apex: choosing Engineering as a apex Skill means being the engine room miracle worker --- when the pilot needs a little bit more V-shift from the motors, he delivers; when the damage seems irrepairable, he gets critical systems back online.

\item[EVA]
the Extra-Vehicular Activity master knows her way around the outside of a spaceship and the equipment needed to do that. Use the EVA Skill to patch a pressure suit, get people into emergency gear fast, hang onto the hull under thrust, or find an obscure way into someone else's space station.

Apex: a specialist in EVA knows everything there is to know about wearable vehicles. Anything you climb into and operate like your own limbs, she is comfortable with it and ready to fight if need be; she is used to working surrounded by lethal environments like vacuum, oceans, ammonia atmospheres, and lethal vegetation leaking poisoned spores; she knows what a WALDO is and how not to hurt herself with it; she can climb the outside of a spaceship under thrust and get back inside safely. When the only safe place is the centimeter between your skin and the inside of the suit, the EVA expert runs the show.

\item[Gunnery (space)]
this Skill gives command over all the many ship's weapon systems, whether torpedoes or beams. It is used to augment weaponry rolls in the space combat system but it can be used outside that system to declare or discover capabilities of examined equipment or to modify existing gear for good or ill.

Apex: the Gunnery specialist is familiar with all forms of ship-to-ship weapons in offensive, defensive, and creative use. Of course he can hit an enemy vessel at a hundred thousand meters with a coilgun battery, but he also knows how to rig a missile as an observation drone or signal with a fusion torch. He's aware of every computer interface and targeting algorithm available for running weapons and he has distinct preference; his customised weapons console is probably incomprehensible to any lesser user.

\item[Intimidation]
sometimes you want to force the other guy to back down or act against his interests and, violent though you may be, you don't feel like shooting him just yet. Intimidation is your first stop before combat. An opposed Intimidation versus Resolve might be used to bluster your way past guards.

Apex: choosing Intimidation as an apex Skill creates a character that is used to getting his way without being right. He can threaten subtly or overtly, bringing to bear knowledge of weapons or bureaucracy, but he always threatens: when he wants something from you, you know you are in danger.

\item[Medical]
low levels reflect basic first aid; advanced levels reflect the skills of a professional surgeon or internist.

Apex: the Medical expert might be a renowned doctor or just an especially skilled Emergency Medical Technician; whichever she is, she gets things done: this person is not by nature a theorist but rather a practical healer of people.

\item[MicroG (combat)]
the facility to move and fight in a very low-gravity environment, such as a ship under low or no thrust or in space. When fighting in these micro-gravity environments, characters use the MicroG Skill instead of the appropriate combat Skill (replacing Agility for movement, and Brawling, Close Combat, and Slug Thrower for doing damage; energy weapons are recoilless and still use the Energy Weapons skill). The MicroG expert must still be trained in the replaced Skill, of course --- no matter what rank his MicroG, he still uses an untrained weapon type at a rank of -1. This makes a MicroG expert a versatile and creative combatant but only in this specialized environment. MicroG could also be used to perform other difficult tasks while in micro-gravity, such as finding a way to get leverage to unjam a warped door or maneuvering to put a ``Spinning out of control'' Aspect on an opponent. Though this Skill supplants combat Skills while in micro-gravity it does not confer any special familiarity with the weapons --- checks to clear jams, disassemble, re-assemble, fix sights, or otherwise manipulate the weapon itself use the appropriate weapon skill.

Apex: the MicroG specialist is completely at home in very low gravity, able to find a grip or brace on any surface and never making ``up-bias'' mistakes --- he'll pick whatever orientation is most advantageous at any time, using recoil to advantage and instinctively ignoring ballistics and coriolis effects. When fighting in close he never makes the mistake of looking for friction leverage, but always fights isometrically, bracing against his opponent and himself.

\item[Navigation (space)]
locating an envelope of space where the slipstream can be entered is tricky business, and the Navigator is the one who knows it inside out. This Skill is used in the space combat system to decide the placement of most ships at the beginning of a fight. Navigation might be used out of combat to plot efficient paths through a system or to find a planetary object that isn't supposed to be there.

Apex: the dedicated Navigation specialist is a cerebral mathematician capable of juggling a thousand variables in a dynamic state with great precision. She knows where things should be, how fast they should be going, and what the fastest or most efficient way through is. She may be well known in some circles and totally unknown in others; it's possible no one anywhere knows her name, but only that she is uncatchable --- or inescapable --- in space.

\item[Oratory]
when you need to be persuasive to a crowd, you need to speak to them with that honeyed voice and careful elocution that makes them want to love you. Use Oratory to rile up a crowd or talk one down.

Apex: the Oratory specialist has made his life's work communication with the masses; his gift is in persuading crowds, taking advantage of rhetorical and emotional tools that make people believe. He's likely well known, his face recognized; he may be a media personality or a politician.

\item[Pilot (space)]
someone has to fly these things! Pilot Skill is used in the space combat system to influence each turn's positioning roll. It also might be used outside of that system to resolve an escape scene quickly or to conduct a complicated orbital maneuver. Pilot Skill refers specifically to the big long-haul reaction drives ship in use for intra- as well as inter-system travel, but not for interface vehicles that ply the space between ground and orbit.

Apex: the hotshot Pilot identifies herself with her craft, understanding that the basics of spaceships are the same no matter where you go or how technology changes. She knows how much further you can push a motor past its design specs, and can tell from the hull vibration just how dangerous a maneuver is; she manages heat and burn so as to gain maximum tactical advantage over other vessels, and is probably in demand by private military ventures and criminals --- everywhere else you can survive with a mediocre pilot.

\item[Profession: \textless~choice~\textgreater]
players choose a profession and can expect to perform any tasks related to that profession using this Skill rank.

Apex: an apex Professional is the best at what he does, gracing the cover of appropriate trade magazines and is sought after for advice by lesser professionals; he is at the cutting edge of his profession's development and speaks frequently at large, very serious gatherings; he may be on committees, setting standards for his area of expertise.

\item[Repair]
the ability to effect mechanical and electronic repairs, excluding computer repairs, weapon maintenance, and spaceship drive maintenance.

Apex: to the Repair expert nothing is broken, just temporarily out of commission; missing parts can be fabricated from substitute materials, broken things can be glued or welded or braced, electronics can be re-purposed from one device to another with just a little logic from this third thing between; she has a tool for every purpose and a box full of minimum essential parts, all adaptable to myriad purposes.

\item[Resolve (track)]
this is how dedicated a character is to his objectives. Just how far is he willing to go? While Resolve primarily determines the length of the Composure stress track, it would also be used to defend against covering fire (defensive roll to oppose a Composure attack with a weapon) or to oppose Intimidation attempts (defensive roll to oppose an Intimidation roll).

Apex: a person with peak Resolve is a cool, cool customer; under the direst of circumstances he does not shake, press the wrong buttons, or make bad choices, but rather he proceeds with his purpose unshaken and all his faculties intact; he is virtually immune to any form of persuasion unless he decides to be persuaded.

\item[Science]
an understanding of the principles of physics, mathematics, chemistry, and biology.

Apex: a character with apex Science Skill is a scientist of some renown --- known, sought after, published, and cited all over the cluster, or at least the system. She knows her field and remains something of a jack-of-all-trades in other fields, bringing her vast knowledge and earnest desire for facts to bear on all problems.

\item[Slug Throwers (combat)]
firearms, whether black powder, cordite, or obscure binary propellants.

Apex: this character is your classic movie gunslinger, familiar with all projectile hurling weapons and their nuances. She can patch ammunition to sabot through too large a barrel, she can overcharge a binary propellant magazine to get better penetration, and she knows ballistics tables better than you know the galley menu after seven years on the same ship. She hits what she aims at every time and has a preternatural intuition for when you are going to expose yourself from cover; she's a killer.

\item[Stamina (track)]
measures the character's general strength and well-being. It is primarily used to establish the length of the character's \Health{} stress track, but would also be checked when exposed to disease (fixed difficulty check) or to lift heavy weights.

Apex: the Stamina specialist is a superman. He eats right, lives well, trains his body, and as a result he finds himself immune to normal disease and able to stress his body almost indefinitely. He's a powerful athlete: a weight lifter, an endurance runner, and an Aphexian buzzclouder. Alternatively, his augmentation may be unnatural, the result of technology rather than good living. He is almost unstoppable by natural means.

\item[Stealth]
this is the Skill for sneaking around, and avoiding notice. Apex: the local equivalent of the mythical ninja, the Stealth specialist is never seen or heard. She is not just hyper-aware of her surroundings and how they make her apparent, but also a master of available technology whether that's light bending meta-material clothing or lampblack. She almost certainly uses her Skills professionally, and it's hard to imagine how that's legal, though she might be an ex-special-forces military professional or perhaps a famous practitioner of an obscure local sport. She always enters the room unnoticed and departs without comment.

\item[Survival]
the ability to survive in the wilderness: building fires, making shelters, surviving hostile environments, etc.

Apex: the Survivalist knows everything there is to know about making the basics of life support from whatever is handy; any dabbler can make do in the wilderness of an earth-like planet for a few months, but this extremist can find air enough in frozen gases to top up his tanks and has the adapter for her suit to do it; she knows what animals you can eat, can make a fire, and can make a lethal trap from something flexible and something sharp. Left alone almost anywhere, she will still be there when you get back.

\item[Tactics]
the ability to make the right choices in the heat of combat. Use your Tactics Skill to place unpleasant Aspects on your opponents as a maneuver (``Out in the open!'') or on the scene (``Fog is rolling in''). The implication is that this was always true, but that the character with Tactics can make it useful to himself and his allies, so now it is an Aspect.

Apex: a character with Tactics as his apex Skill is a master at moving men through hostile situations --- he always chooses the best cover, times his actions at the expense of his opponents, and provides the best advice; he's probably a military man or a member of an elite police unit and he's seen combat before.

\item[Vehicle]
the ability to drive all terrestrial vehicles, on land and water.

Apex: the character with Vehicle as his apex Skill is able to drive practically anything as long as gravity (or an artificial equivalent) is pinning the bottom of the vehicle to something. He's the go-to person for getaways and pursuits planetside.
\end{description}

