\section{Aspects}\label{sec:aspects}  %\href{sec:id59}

\input{sidebar/summary-aspects}

All characters and some things will have \Aspects. These short phrases indicate 
what is important about the character. Scenes might have \Aspects, maps might 
have \Aspects, systems, worlds, and cities might all have \Aspects. Give a 
thing an \Aspect\ when you want it to have a feature but don't need a specific 
rule mechanism to govern how that feature operates. Instead you are declaring 
that something is important and leave it to players to determine how to make 
it important.

% \vfil
\subsection{What do Aspects do?}\label{sec:what-do-aspects-do} %\href{sec:id60}

There are a number of ways that \Aspects\ come into being, and a number of 
ways they can be used during conflict (whether that's just a skill check 
during regular role-play or a specific roll in a combat sequence).

\rulebox{
Any time you roll the dice, you could bring \Aspects\ into play.
}

\subsubsection{invoking aspects}

You can \emph{invoke}\index{aspects!invoking} one of your own \Aspects\ 
\emph{after} you roll the dice. You narrate how the \Aspect\ affects the roll 
and, assuming everyone at the table nods assent and says \emph{that's cool,} 
you can add +2 to your roll or else re-roll. You pay a fate point immediately.

\subsubsection{tagging aspects}

\input{sidebar/aspects}

You can \emph{tag}\index{aspects!tagging} an \Aspect\ on something else that's 
relevant to the roll \emph{after} you roll the dice. That could be an \Aspect\ 
on your opponent, an ally, on a map  or any other \Aspect\ that's relevant and 
not on your character. Take +2 on your roll or else re-roll. You pay a fate 
point immediately.

\subsubsection{compelling opponent aspects}

You can \emph{compel}\index{aspects!compelling} an \Aspect\ on your opponent 
\emph{before} you roll the dice. In this case you offer your opponent a deal 
related to his \Aspect: he can take the deal and one of your fate points or 
deny the deal and give you a fate point. Outside of a combat sequence the deal 
can be quite free-form and it is a negotiation between \emph{players} and not 
between characters. You might offer the Referee a deal relating to an NPC, a 
deal relating to an ally or most commonly a deal offered by the Referee to a 
character's player. During a combat sequence the effects of a compel are far 
more constrained (and dealt with in detail in the appropriate section).

\subsubsection{compelling other aspects}

You can \emph{compel} an \Aspect\ on a scene or zone (or anything for that 
matter). You offer the Referee a deal related to the \Aspect: he can take the 
deal and one of your fate points or deny the deal and give you a fate point. 
In or out of combat, the deal is free-form and it is a negotiation between 
\emph{players} and not characters. You might offer the Referee a deal relating 
to any scope as mentioned in the ``Aspect scope'' section.

\subsection{Aspect scope}

As mentioned above, any character, vehicle, location, object, story arc or 
anything else may have \Aspects. For any given \Aspect, the ``thing'' the 
\Aspect\ belongs to is called the \Aspect's \emph{scope}. You may only tag one 
\Aspect\ on each related \emph{scope}\index{aspects!scope} per roll. In some 
cases additional scopes may be added during play, but some sample \Aspect\ 
scopes are:

\begin{itemize}
\item yourself
\item Opponent
\item System
\item Scene
\item Zone
\item Ship
\item Campaign
\item Ally
\end{itemize}

In addition, any number of free-taggable\index{aspects!free tags} Aspects from any scope may be tagged and don't count against your tagging limit (that is, you can tag two free-taggables at zone scope and still tag a third if there is one for the usual fate point cost).

\subsection{Where do Aspects come from?}

Aspects come into being in several ways:
\begin{itemize}
\item player characters start with 10 Aspects derived from the character generation stories. They get a \emph{fate refresh} of 5 fate points at the beginning of a session.

\item spaceships start with 5 Aspects\index{spaceships!aspects!starting amount} created by the designer (some forced by the design process). They start each session with five fate points.\index{aspects!on spaceships}\index{spaceships!fate points!starting amount}

\item scenes, maps, campaigns, and things get Aspects at the discretion of the referee.\index{aspects!on scenes}\index{aspects!on maps}\index{aspects!on campaigns} The referee has an unlimited supply of fate points.

\item players can put an Aspect on a character or scene with a \textbf{Maneuver}.
\end{itemize}

\subsection{Maneuvers}\label{sec:maneuvers} % \href{sec:id61}

A maneuver\index{maneuver} is an action your character takes that will change the status of something and this status change will be represented by the addition of an Aspect. The referee will decide what to roll (either a \nameref{sec:fixed-difficulty-roll} or an \nameref{sec:opposed-roll} --- see the \nameref{sec:resolution} section) and on success the target acquires an appropriate Aspect.\index{aspects!from maneuvers}

Having an Aspect of your choosing placed on an enemy is pretty powerful all by itself, but there is an additional power: an Aspect placed as a result of a maneuver can be tagged \emph{without paying a fate point} once by the maneuverer or an ally (it is \emph{free-taggable}).\index{maneuver!and free tags} It can be tagged normally subsequently as long as the Aspect lasts, but the first time (and only the first time) is free.

\rulebox{
Place an Aspect on an opponent or a scene with a Skill check
}
(static or opposed, as determined by the referee). If successful, the target now has the Aspect.\index{aspects!from skill checks} This Aspect can be tagged once for free and thereafter for a fate point.

