\section{Equipment}
\label{sec:Equipment}

Characters should be considered to start with whatever equipment is relevant to their Skills and any trivial equipment should be present if needed unless lacking the item advances the plot. The only equipment that is guaranteed to be with the character when they need it is equipment that is represented by a ``Have a thing'' Stunt.

The referee cannot take away equipment specified as a Stunt from a player's character unless the player agrees and the Stunt is changed. This does not imply that an owned spacecraft (through a Stunt) cannot be Taken Out in combat, but rather that Taken Out cannot mean total loss of the craft with no chance of repair or replacement, unless the owning player agrees.

Rather than itemizing in a list, starting gear is assumed based on the Skills players select for their characters; quality of gear might also be affected by the Skill level: a character with EVA 1 might have an old T1 suit worn by her father; a character with EVA 4 might have a sleek T3 suit, custom fitted.

\subsection{Automatic Skill Gear}
\label{sec:automatic-skill-gear}

\input{tables/automatic-skill-gear}

Some Skills imply access to some kinds of equipment. Below are a list of associations that one can afford to take for granted, though, unless the equipment is represented by a ``Have a thing'' Stunt, it's not guaranteed to always be with the character --- it can be lost or destroyed. This list can be extended, according to the decision of the table: the standard is \emph{whatever's reasonable}.

Nothing guarantees the continued presence of the equipment, unless there is also an Stunt to cover it.

Many people will want the highest technology gear for their characters, and it is worth keeping track of the technology rating of anything purchased, if only because that can possibly serve as an Aspect at moments of crisis. Nevertheless, things do not stay at the same quality once they are invented, and a T3 hand computer will be far superior to a T0 one.

Creativity can be rewarded, especially when the benefits come at the level of role-playing, rather than at the level of the specific combat sub-games. A highly advanced knife might not do any more damage, but perhaps is made of a memory plastic --- when inactive, it is a simple cylinder of plastic but becomes activated by smacking it against a hard surface, and the cylinder deforms to become a hard, sharp, combat blade.

Similarly, an energy weapon might have a biometric check associated with it, allowing only the owning player to use it (this would be similar to making the weapon integral). Something like this might be hard to find, and it may be illegal, but it does not require a special Skill or Stunt to use.

