\chapter{Space Combat}\label{sec:space-combat} % \href{sec:id136}

\input{sidebar/original-material-space-combat}

Spacecraft are large, relatively fragile things pursuing their goals at high velocity in the dead of space. They are constrained by their available reaction mass, the mass  allocated for trade cargo, and their ability to dissipate heat. When they test each other to destruction using the assorted weapons of space combat --- beams, torpedoes, and electronic warfare --- they are chiefly pursuing goals of domination or escape. This system emphasizes these goals. The stories we want to tell include:

\begin{itemize}
\item an inferior ship escaping from the authorities
\item a hostile vessel capturing cargo
\item a threat so powerful the only real option is to surrender
\item a convoy of merchants and escorts safely defending itself from marauders
\end{itemize}

Space combat occurs on a simple map that emphasizes pursuit in order to provide a simple and fast system.

Combat occurs in phases. First is the detection phase which establishes the initial positions. Then the positioning, electronic warfare, beams, torpedoes, and damage control phases are repeated in order until everyone is happy, dead, or escaped. Order of action is controlled by social pressure: a player is designated caller for the fight and that person controls the transition from phase to phase (see sidebar on ``Social Initiative''). If a player wants to act in a particular phase, he announces his action. The advantage of going first goes to the one that speaks first. The advantage of going last goes to the person who speaks last. When the caller calls for a change of phase, it is possible that some players failed to act in time.

\input{chapter/06/sec-the-crew}
\input{chapter/06/sec-spacecraft}
\input{chapter/06/sec-the-map}
\input{chapter/06/sec-social-initiative}
\input{chapter/06/sec-the-sequence}
\input{chapter/06/sec-damage}
\input{chapter/06/sec-special-maneuvers}
\input{chapter/06/sec-wargaming}
