\chapter{Social Combat}
\label{cha:social-combat}
\vfil

Social combat can be used to handle complicated social and personal situations. It adds a clear objective, so you can avoid spending a lot of energy talking fruitlessly in character when no real strategies for resolution present themselves. It gives the same opportunities to make interesting narration as the regular combat system, wrapped up in a tactical challenge.

To begin, set the stakes: establish clearly what happens if the characters win and what happens if they lose. Stakes might be ``We get the location of the secret base'' or ``We get to make a \skill{Science} roll to determine how much about the base we get to narrate'' or ``I get the girl'' or something entirely different. Losing could simply indicate failure to achieve these things, but the referee should be creative in establishing real (but interesting) losses --- failure perhaps earns the enmity of the girl's family or gets your license to practice medicine revoked.

Once the stakes are established, establish victory conditions, which depend on the map (\autoref{sec:social-combat-map}).

% badbox here
% \newpage
% \vfil

Usually the only stress track that gets action in social combat (and it doesn't need to) is the \Composure{} track on individual characters. In some cases it might make sense to place the \Wealth{} stress track at risk instead or as well, but this is at the discretion of the referee when designing the conflict.

% \vspace{\fill}

\input{chapter/07/sec-the-map}
\input{chapter/07/sec-the-sequence}
\input{chapter/07/sec-damage}

% \vfil