\chapter{Platoon Combat}
\label{cha:platoon-combat}
% \vfil

\input{sidebar/military-organization}

The rules for platoon-scale wargaming are provided in Diaspora for campaigns that want to focus on military combat. Perhaps the players are old army buddies, offering their services to their planet's defense. Perhaps a heavily balkanized world is enlisting off-worlders to fight their battles for them. Perhaps the characters are a mercenary strike team, performing short-term contracts for anyone willing to pay. Whatever the story, it is easy to imagine combats where the scale of personal combat is simply inadequate: when there are too many individuals active in battle, platoon scale provides opportunities for incorporating infantry, artillery, armour and aircraft units in a ground war.

% \vfil

Some campaigns may choose to build around this sort of encounter, with the story effectively moving the characters from one mercenary ticket to the next with each game session. Others might never need these rules, but will be able to occasionally use them to model robbing an armoured vehicle.
%
% \vfil
\iflandscape{\newpage}{}

%
Whatever the application, the rules are provided as a means of representing something that could also be done within the existing Diaspora mechanisms. Operating at the platoon scale becomes an option that is available for those tables that want it.

% \vfil

The organizational unit of interest is the platoon. This is a number of single units, one of which is a leader, all in communication. The only stress track used is the \Morale{} stress track of individual units.

For infantry units, platoon scale represents combat between teams of 2-5 soldiers organized into platoons of 2-6 teams; an armour platoon might be 4 or 5 tanks. Individual characters can improve a platoon's performance, but, as in space combat, an individual can only modify the performance of the larger unit. The principles of FATE still apply, of course, and (as is common in Diaspora), they have been stripped down.

At the platoon scale, there is only a single stress track: \Morale. If a platoon loses morale, it can no longer function. Whether it has lost morale because of its ongoing frustration with lack of supply lines, because of the constant pressure of close enemy fire, or simply because most of the platoon has been killed, Diaspora models the only crucial variable of loss at the platoon scale along the axis of morale.

In most games, players will control either a single platoon, or (as is more usual when used as a stand-alone game) a company of 3-5 platoons.

As with the other mini-games, platoon-scale war-gaming can be played independent of the larger Diaspora RPG.

% \vfil
% \newpage

\input{chapter/08/sec-the-map}
\input{chapter/08/sec-command}
\input{chapter/08/sec-units}
\input{chapter/08/sec-the-sequence}
\input{chapter/08/sec-damage}
\input{chapter/08/sec-characters-in-platoon-combat}
\input{chapter/08/sec-wargaming}
