%%% Sec. 4.1
\section{The Refresh}
\label{sec:the-refresh}

The first few minutes of every session are set aside to manage some accounting and preparation that needs to take place before actually getting down to the game. This is called the refresh. In FATE this is when you get your fate points assigned for the session. In Diaspora there is some more going on.

Occasionally a session will narrate away large blocks of time as downtime. It's perfectly reasonable for the referee to offer one or even several refreshes to let the players decide how this time has affected their characters. A referee may grant two or three refreshes to the players to indicate major life changes that take place over several months.

\subsection{Fate Points}
\label{sec:Fate Points}

Assign fate points for each character and each spacecraft. Characters get five fate points each. Fate points are not recorded between sessions, so at the refresh all characters start with five no matter how many they ended the last session with. Spacecraft similarly get five fate points.

Players usually regain fate points between sessions, when a refresh occurs. If the referee left things at a cliffhanger, he is entitled to say that no refresh has occurred between sessions. By the same token, if the referee feels that a substantial amount of downtime and rest occurs in play, a refresh of fate points may occur mid-session. Normally each character starts each session with exactly five Fate points.

\subsection{Experience}
\label{sec:Experience}

Players may make adjustments to their characters to represent changes and experience as a result of the last session. During the refresh, a player has the option to change his character in three ways.

\begin{enumerate}
\item A player may move any Skill up the Skill pyramid one place (though not past level 5) and then must move a Skill from that new rank down one level. This must maintain the Skill pyramid, always having one Skill at rank five, two at rank four, and so on.

\item A player may change an underused Aspect for an Aspect relating to in-game events from previous sessions.

\item A player may exchange one Stunt.
\end{enumerate}

Characters may therefore change from one session to the next, and can develop Skills and interests as time progresses. Nevertheless there is clear continuity from one session to the next.

\subsection{Healing \& Repairs}
\label{sec:healing-and-repairs}

Characters should be checked to see if they qualify for any healing. Specifically, any severe \Consequences\ that have been carried completely through the last session (that is, they were inflicted the session before the last session) can finally erase that consequence. All \Health\ and \Composure\ stress is cleared. \Wealth\ stress might be cleared.

If the session begins at an appropriate facility, any spacecraft may make a maintenance roll now using modifiers based on the prior session (for determining whether the vessel was engaged in trade, and so on).

\subsubsection{Stress Track Recovery}
\label{sec:Stress Track Recovery}
%%%TODO put tables here?

Downtime can remove the accumulated effects of hits to the \Health\ and \Composure\ tracks.

\rulebox{\Health\ and \Composure\ stress tracks are cleared any time there is a refresh.}

\Wealth\ stress box hits don't go away as easily as other stress.
\rulebox{\Wealth\ stress track hits are cleared at the end of any session in which the character takes no hits or \Consequences} against his \Wealth\ stress track. See the section on \nameref{sec:debt-and-solvency}, below, for details.

\subsubsection{Removing Consequences}
\label{sec:Removing Consequences}

\Consequences\ fade with time. How long this takes depends upon the severity of the \Consequence, which in turn depends upon how it was received.

\begin{description}
\item [Mild Consequences] are removed any time the character has the opportunity to sit down and take a breather for a few minutes. These \Consequences\ will usually last until the end of the current scene, unless there is no break between scenes.

\rulebox{Mild \Consequences\ are removed at the end of the scene.}

\item [Moderate Consequences] require the character get a little more time and distance. A good night's sleep or other extended period of rest and diversion is required.

\rulebox{Moderate \Consequences\ are removed at every refresh.}

\item [Severe Consequences] linger for at least the entire session following the one it was received. That session should contain a month or so of in-game time explicitly spent recuperating.

\rulebox{Severe Consequences are carried through one complete session} (from beginning to end) in which the stress track associated with the \Consequence\ does not take any hits, and are removed at the next refresh.
\end{description}
