\section{Units}\label{sec:Units}
\iflandscape{\vfil}{}


A unit is the minimum element represented on the map for each type: a single miniature or counter. For infantry, that's a team of a few soldiers. For armour that's one vehicle. For artillery that's a battery.

There are four types of team units: infantry, artillery, armour, and aircraft. For each platoon, one unit (which may not be aircraft) is also designated the leader. There is no maximum number of units in a platoon.

Each unit in a platoon grants the platoon one fate point. All fate points are kept on the platoon and spent from the platoon. All Consequences are on the platoon.

Similarly, spin counters are associated with platoons and not with units. They may be spent by any unit in the platoon. Spin expires after having had one complete turn in which to use it (thus if spin is acquired during a defensive roll, it lasts until the end of the platoon's next opportunity to act whereas if it is acquired during movement, say, it lasts until the end of the platoons next opportunity to act and not the opportunity in which it moved).

Units that are not normally part of a platoon (typically aircraft) are associated with a particular platoon and donate their fate point to that platoon. They draw fate points from that platoon when invoking, tagging, or compelling.

All units have Skills, Aspects, Stunts, and a \Morale\ stress track. Skills are an n-cap pyramid (i.e. one Skill at level three, two Skills at level two, and three Skills at level one) or a column (i.e. one Skill at level four, one Skill at level three, one Skill at level two, and one Skill at level one).

All units have one Aspect and contribute one fate point to their platoon. Infantry units have a baseline of zero Stunts, plus one Stunt for each technology level. All other units have one Stunt, plus one additional Stunt for each technology level; consequently, units at T-1 or lower do not have Stunts. As described below, the platoon leader always has one additional Stunt, regardless of technology level. No unit may have negative Stunts.

Units have only one stress track: \Morale. When a unit takes a hit past the end of its \Morale\ track that cannot (or will not) be mitigated by a platoon \Consequence, it is eliminated. The narrative associated with this elimination can be determined by the table: it might represent panic and dispersal or surrender; a complete lack of morale is also adequately explained by everyone being killed. Some combination of the three is most likely.  The mechanical effect at this scale is the same. As with other stress tracks, a hit on a marked box rolls up to the next unmarked box.

\input{chapter/08/subsec-skills}
\input{chapter/08/subsec-stunts}
\input{chapter/08/subsec-stress-tracks}
\input{chapter/08/subsec-aspects}
\input{chapter/08/subsec-infantry}
\input{chapter/08/subsec-armour}
\input{chapter/08/subsec-artillery}
\input{chapter/08/subsec-aircraft}
\input{chapter/08/subsec-leadership}
\input{chapter/08/subsec-typical-units}


