\subsection{Typical Units}
\label{sec:typical-units}

\input{units/typical-units}

\vfil

\subsubsection{Typical Infantry}

Skill tree: Camouflage 3, Direct Fire 2, Observation 2, Armour 1, Hand to-Hand 1, Command 1.

Infantry are used to capture and hold territory as well as to provide spotting for heavier units.  They have NCOs capable of regrouping broken units and are adept at close combat as well as ranged. They excel at not being seen.

\subsubsection{Typical Armour}

Skill tree: Armour 4, Direct Fire 3, Movement 2, Anti-air 1.

There are two core types of armour: assault tanks designed to move into heavy fire and attack units spotted by associated infantry, and tank hunters, which would swap Armour and Direct Fire.

\vfil

\subsubsection{Typical Artillery}

Skill tree: Indirect Fire 3, Camouflage 2, Movement 1.

Artillery's immediate objective is to destroy spotted enemy equipment. It does so by projecting a huge volume of fire, which makes it suddenly very vulnerable. It offsets this vulnerability by immediately moving and re-hiding.

\subsubsection{Typical Aircraft}

Skill tree: Direct Fire 4, Observation 3, Anti-air 2, Movement 1.

Aircraft Skill trees are capped by their primary design goal --- Direct Fire for ground attack vehicles, Observation for reconnaissance craft, and Anti-air for interceptors. Most aircraft will be capable in all of these. Movement for aircraft indicates their re-arm time --- high Movement rates indicate rapid re-arming cycles, trading off for specialty effectiveness such as ground attack or anti-air capability.
